### 2015-03-30 swmpr_manu.Rnw
Fixed title case in title, some examples still had left over arguments from old plot methods

% Title must be 250 characters or less.
% Please capitalize all terms in the title except conjunctions, prepositions, and articles.
\begin{flushleft}
{\Large
\textbf\newline{SWMPr: An R package for Retrieving, Organizing, and Analyzing Environmental Data for Estuaries}
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Marcus William Beck\textsuperscript{1, *}

@@

# plot raw and smoothed
plot(dat, type = 'l')
lines(dat_smooth, select = 'do_mgl', col = 'red', lwd = 2)
@

>>>>

% Title must be 250 characters or less.
% Please capitalize all terms in the title except conjunctions, prepositions, and articles.
\begin{flushleft}
{\Large
\textbf\newline{SWMPr: An R Package for Retrieving, Organizing, and Analyzing Environmental Data for Estuaries}
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Marcus William Beck\textsuperscript{1, *}

@@

# plot raw and smoothed
plot(dat)
lines(dat_smooth, col = 'red', lwd = 2)
@

### 2015-03-30 swmpr_manu.tex
Fixed title case in title, some examples still had left over arguments from old plot methods

\begin{knitrout}\small
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{kframe}
\begin{verbatim}
> # import data, qaqc and subset
> data(apadbwq)
> dat <- qaqc(apadbwq)
> dat <- subset(dat, select = 'do_mgl', 
+   subset = c('2012-07-09 00:00', '2012-07-24 00:00')
+   )
> 
> # smooth
> dat_smooth <- smoother(dat, window = 50, params = 'do_mgl')
> 
> # plot raw and smoothed
> plot(dat, type = 'l')
> lines(dat_smooth, select = 'do_mgl', col = 'red', lwd = 2)
\end{verbatim}
\end{kframe}\begin{figure}[!ht]

>>>>

\begin{knitrout}\small
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{kframe}
\begin{verbatim}
> # import data, qaqc and subset
> data(apadbwq)
> dat <- qaqc(apadbwq)
> dat <- subset(dat, select = 'do_mgl', 
+   subset = c('2012-07-09 00:00', '2012-07-24 00:00')
+   )
> 
> # smooth
> dat_smooth <- smoother(dat, window = 50, params = 'do_mgl')
> 
> # plot raw and smoothed
> plot(dat)
> lines(dat_smooth, col = 'red', lwd = 2)
\end{verbatim}
\end{kframe}\begin{figure}[!ht]
